---
title: "Homework 6, Amelia Grant-Alfieri, ag3911"
output: github_document
---

#Problem 1

Analyzing homicide data in the United States. 

##Tidy Data and Create New Variables

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and  non-white, with white as the reference category. Be sure that victim_age is numeric.

```{r}
```

##Logistic Regression Model for Baltimore, Maryland

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 

Save the output of glm as an R object

apply the  broom::tidy to this object

obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r}
```

##Logistic Regression for Each City 

run glm for each of the cities in your dataset and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and  unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
```

##Plot Estimated Odds Ratios and Confidence Intervals for Each City 

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
```


#Problem 2

Understanding the effects of several variables on a child’s birthweight. 

##Load and Tidy Data

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
```

##Birthweight Regression Model #1

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

Describe your modeling process. 

Show a plot of model residuals against fitted values (use  add_predictions and add_residuals in making this plot).

```{r}
```

##Compare Model #1 to Two Different Models

###Model #2
Make a second model using length at birth and gestational age as predictors (main effects only).

```{r}
```

###Model #3

Make a third model using head circumference, length, sex, and all interactions (including the three-way interaction) between these. 

```{r}
```

###Compare Models #1 and #2

Make this comparison in terms of the cross-validated prediction error; use  crossv_mc and functions in purrr as appropriate.

```{r}
```

###Compare Models #1 and #3

Make this comparison in terms of the cross-validated prediction error; use  crossv_mc and functions in purrr as appropriate.

```{r}
```

