---
title: "Homework 6, Amelia Grant-Alfieri, ag3911"
output: github_document
---

# Problem 1: Analyzing homicide data in the United States. 

## Tidy Data and Create New Variables
  * create a city_state variable (e.g. “Baltimore, MD”)
  * create a binary variable indicating whether the homicide is resolved. 
  * omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race  
  * omit Tulsa, AL – this is a data entry mistake
  * modifiy victim_race to have categories white and non-white, with white as the reference category
  * be sure that victim_age is numeric.
  
I defined resolved as closed with arrest. 
```{r message=FALSE, output=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(tidyr)
library(stringr)
library(forcats)
library(dplyr)
library(plyr)
library(stats)
library(purrr)
library(broom)
library(ggplot2)
getwd()

tidy = read_csv("./homicide-data.csv") %>%
  select(victim_age, victim_race, victim_race, victim_age, victim_sex, city, state, disposition) %>%
  filter(city != "Dallas", city != "Phoenix", city != "Kansas City") %>%
  mutate(Tulsa_AL = (state == "AL" & city == "Tulsa")) %>%
  filter(Tulsa_AL == FALSE) %>%
  filter(victim_age != 102, victim_age != 101) %>%
  filter(victim_race != "Unknown" | victim_race == "NA") %>%
  filter(victim_age != "Unknown", victim_sex != "Unknown") %>%
  mutate(city_state = str_c(city, ", ", state),  #new var combines city and state
         #resolved = recode(disposition, 
                          #`Closed by arrest` = "resolved",
                          #`Open/No arrest` = "unresolved",
                          #`Closed without arrest` = "unresolved"), 
         resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", "white", "nonwhite")) %>%
         #victim_race = relevel(victim_race, ref = "white"))
         #victim_race = as.numeric(victim_race),
         #resolved = as.numeric(resolved),
         #victim_sex = as.numeric(as.factor(victim_sex))) %>%
  select(-city, -state, -Tulsa_AL, -disposition)

#mutate(victim_race = as.numeric(victim_race == "non-white")) #white is 0, non-white is 1
#after re-leveling a var, do i have also to convert it to numeric? 
```

## Logistic Regression Model for Baltimore, Maryland
  * For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs  unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
  * Save the output of glm as an R object
  * apply the  broom::tidy to this object
```{r output=FALSE}
baltimore = tidy %>%
  select(resolved, victim_age, victim_race, victim_sex)

balt_fit = 
  baltimore %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
```

Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.
```{r} 
balt_fit %>%  
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  filter(term == "victim_racewhite") %>%   #for some reason victim_racenonwhite isn't showing up, i might have made a mistake making nonwhite as the reference instead of white 
  select(term, log_OR = estimate, std.error, OR) %>% 
  mutate(conf.high = exp(log_OR + 1.96*std.error),  
         conf.low = exp(log_OR - 1.96*std.error)) %>%
  knitr::kable(digits = 3)
```
The adjusted odds ratio is 1.68 with a 95% confidence interval of (1.587, 1.780). 


## Logistic Regression for Each City 

Run glm for each of the cities in your dataset and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and  unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
all_city = tidy %>%
  group_by(city_state) %>%
  nest() %>% 
  filter(city_state == "Baltimore, MD") %>%
  mutate(output = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = tidy, family = binomial())), 
         output = map(output, broom::tidy)) %>%
  select(-data)
```

## Plot Estimated Odds Ratios and Confidence Intervals for Each City 

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
plot = all_city_OR %>%
  group_by(city_state) %>%
  #mutate(estimate = as.numeric(estimate)) %>%
  #arrange(city_state, desc(estimate)) %>%
  ggplot(aes(x = reorder(city_state, -log_OR), y = log_OR)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, width = 0.2)) + geom_point() + labs(x = "Location", y = "log-transformed Odds Ratio", title = "The Odds of Solving Homicides for Non-White compared to White Victims by City, State") + theme(axis.text.x = element_text(angle = 90))
plot
```
comment on the plot


# Problem 2: Understanding the effects of several variables on a child’s birthweight. 

## Load and Tidy Data

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r message=FALSE}
p2_tidy = read_csv("./birthweight.csv") %>%
  janitor::clean_names() %>%
  select(bwt, blength, gaweeks, bhead, babysex) %>%
  mutate(babysex = as.factor(babysex), 
         gaweeks = as.numeric(gaweeks)) %>%
  mutate(babysex = recode(babysex, `1` = "male", `2` = "female")) 
```

## Birthweight Regression Models

### Model #1

My proposed model uses gestational age (in weeks) as a predictor of birthweight. In general, premature babies, those with a younger gestational age in utero, weigh less than full-term babies. This relationship is supported biologically by the rapid growth and weight gain a fetus is supposed to undergo during the final trimester in utero. 
```{r}
library(tidyverse)
library(modelr)
library(mgcv)

model_1 = lm(bwt ~ gaweeks, data = p2_tidy) 
  broom::tidy() 
```

Plot of model of residuals against fitted values using  add_predictions and add_residuals.
```{r}
model_1_plot = p2_tidy %>%
  modelr::add_residuals(model_1) %>%
  modelr::add_predictions(model_1) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point()
model_1_plot
  ggplot(aes(x = gaweeks, y = bwt)) + geom_point() + geom_line(aes(y = resid), color = "red") + geom_line(aes(y = pred), color = "blue") + labs(x = "gestational age (weeks)", y = "birthweight (grams)", title = "Gestational Age and Birthweight")
model_1_plot
```
Model #1 shows a positive relationship between gestational age and birthweight. There is little data on gestational age earlier than 30 weeks, which makes sense because babies delivered at that time would be extremely underdeveloped. The residual is fairly randomly dispersed along the horixontal axis, indicating that this model is a decent fit for the data.   

### Model #2

The second model uses length at birth and gestational age as predictors (main effects only) of birthweight. 
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = p2_tidy) %>%
  broom::tidy() 
```

### Model #3

The third model uses head circumference, length, sex, and all interactions (including the three-way interaction) as predictors of birthweight. 
```{r}
model_3 = lm(bwt ~ bhead + babysex + blength + bhead*babysex + bhead*blength + bhead*babysex*blength + blength*babysex, data = p2_tidy) %>%
  broom::tidy() 
```

### Compare Models #1 and #2

Compare in terms of the cross-validated prediction error (use crossv_mc and functions in purrr as appropriate).
```{r}
cv_12 = crossv_mc(p2_tidy, 100) %>%
  mutate(model_1 = map(train, ~lm(bwt ~ gaweeks, data = p2_tidy)),
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = p2_tidy))) %>%
  mutate(rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))

cv_12 %>%
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + labs(y = "Root Mean Squared Errors (RMSE)", x = "Model", title = "Model 1 and 2 Comparison")
```
Model #2 appears to be a better fit for the data because it has a smaller RMSE than Model #1. 

### Compare Models #1 and #3

Compare in terms of the cross-validated prediction error (use crossv_mc and functions in purrr as appropriate).
```{r}
cv_13 = crossv_mc(p2_tidy, 100) %>%
  mutate(model_1 = map(train, ~lm(bwt ~ gaweeks, data = p2_tidy)),
         model_3 = map(train, ~lm(bwt ~ bhead + babysex + blength + bhead*babysex + bhead*blength + bhead*babysex*blength + blength*babysex, data = p2_tidy))) %>% 
  mutate(rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

cv_13 %>%
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + labs(y = "Root Mean Squared Errors (RMSE)", x = "Model", title = "Model 1 and 3 Comparison")
```
Model #3 appears to be a better fit for the data because it has a smaller RMSE than Model #1. 
